# Resolved Issues

## Patch 1.2 - 2/13/15

### Identified Issues
We recently released a patch to address the system version of python being v2.6.6. 
The patch upgrades the python distribution on the image to v2.7.9 while still maintaining the CentOS 6.6 package manager yum's dependency on python v2.6.6.

### Affected Version
These issues only affect users on `UIUC_IMAGE_VERSION='STAT490 Image Version: 1.1'`. 
To tell if you are on this image, type into shell:

```{r uiuc_image_version, engine='bash'}
echo $UIUC_IMAGE_VERSION
```

If the returned value is blank, you are on `STAT490 Image Version: 1.0` and must apply `patch1_1.sh` before continuing.

If the returned value is equal to `STAT490 Image Version: 1.1`, then you can apply the patch.

If the returned value is greater than or equal to `STAT490 Image Version: 1.2`, then you have already applied the patch.


### Applying the Patch

To apply the patch, login as root and run:
```{r bash_patch, engine='bash'}
# Obtain Script
wget https://raw.githubusercontent.com/coatless/stat490uiuc/master/install_scripts/patches/patch1_2.sh
# Set run permissions
chmod u+x patch1_2.sh

# Launch Script
./patch1_2.sh
```


## Patch 1.1 - 1/23/15

### Identified Issues
We recently released a patch to address four issues: 

1. Lack of SSH support for `rstudio`
2. Lack of `UIUC_IMAGE_VERSION` variable.
3. Environmental variables not being accessible by children of the current process.
4. Removal of installation script and patch scripts.  

### Affected Version
These issues only affect users on `UIUC_IMAGE_VERSION='STAT490 Image Version: 1.0'`. 
To tell if you are on this image, type into shell:

```{r uiuc_image_version, engine='bash'}
echo $UIUC_IMAGE_VERSION
```

If the returned value is blank, you are on `STAT490 Image Version: 1.0`.

If the returned value is equal to `STAT490 Image Version: 1.1`, then you have already applied the patch

If the returned value is greater than `STAT490 Image Version: 1.1`, then you are living in the future and should share with me the future code that I will write.

### Applying the Patch

To apply the patch, login as root and run:
```{r bash_patch, engine='bash'}
# Obtain Script
wget https://raw.githubusercontent.com/coatless/stat490uiuc/master/install_scripts/patches/patch1_1.sh
# Set run permissions
chmod u+x patch1_1.sh

# Launch Script
./patch1_1.sh
```
